%!TEX root = EDDF_Pilot_Briefing.tex

\section[general]{General}

\subsection[apron]{On the Apron}

\begin{itemize}
  \item \underline{Always have charts available!}\\ 
    Frankfurt is a complex airport and you will not be able to find your way without charts! 
    The easiest way to find some charts: just google “EDDF charts” or visit vats.im/eddf-charts! 
    
  \item \underline{Callsign:} Frankfurt Apron (not Ground!)
  
  \item \underline{Taxi on N and L:}\\ 
    25 in use: L to the east (RWY 25C), N to the west (RWY 18)\\ 
    07 in use: L to the west (RWY 07C/18), N to the east (Gates)\\
    (the controller may deviate from this due to operational reasons)
    
  \item \underline{Holdshort Instruction:}\\
    Frankfurt Apron is complex and many hold short instructions are possible. 
    If you are given a hold short of instruction: Hold in front of the dashed yellow line, do not turn into the taxiway! See the example image below:
    
    % Bild N10 Clearence Bar!
    
  \item \underline{Blue and Orange Lines:}\\
    Used for aircraft up to a size of A321/B739 that they can taxi next to each other instead of the yellow line. 
    These lines are located on N south of Terminal 2 and at N7 between N and L (see image below). 
    
    % Bild N-blue/orange
    
  \item \underline{Giveway Instruction:}\\
    Often you will hear an instruction to \textbf{continue taxi as number two behind a passing aircraft} 
    (\emph{e.g. “Taxi via N8 N, hold short of N10, at November number 2 behind company A320 from left”}).\\ 
    This means, you have to give way to this aircraft at the crossing taxiway. 
    Please make sure to follow these instruction correctly, otherwise ask the controller if the mentioned traffic is not in 
    sight or you are unsure what to do.
    
  \item \underline{Links at N8 and N7:}\\ 
    “Links” are used to connect taxiway N7 and N8 at different locations. 
    These are really important for the traffic flow, and are used quite often (see images). 
    If you are unsure what to do you should always ask the controller to avoid a face to face situation with other aircraft. 
    These Links are published at all charts, you may have to look at the “parking stands” chart to find them!
    
    % Bilder der Links einfügen!

\end{itemize}

\subsection[tower]{Tower}

\begin{itemize}
  \item \underline{Stopbars:}\\ 
    At U, T and Y there are named stopbar to protect the extended centerline of the runways (see image below). 
    The name of such a stopbar can be seen at all common charts. 
    Inbound traffic is usually told to hold short of T4 on taxiway T.\\ 
    \textbf{Do not cross this stopbar without clearance by ATC!}
    
    % Bild Stopbar T4!
    
\end{itemize}
